An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 Revision/response.tex

\noindent
\textbf{Response:} 
Thank you for your suggestion. We fully understand your concern regarding our use of synthetic or less meaningful attributes in the hybrid query experimental setup.

We  try to find suitable e-commerce datasets to better align with the application scenarios mentioned in the introduction. We investigated some publicly available e-commerce datasets, such as ecommerce\_product\_images\_18K and MEP-3M datasets. However, we found that neither of these datasets fully met our requirements for conducting hybrid querying experiments.
Specifically, the ecommerce\_product\_images\_18K dataset was too small to effectively evaluate the performance and scalability of hybrid querying algorithms under large-scale datasets. On the other hand, while the MEP-3M dataset was larger, it did not directly provide image data that could be encoded into vectors, and we were unable to find suitable fields for vectorization.
As we were unable to locate an ideal e-commerce dataset that simultaneously contained sufficient scale of both vectors and structured attributes, we ultimately decided to continue using the WIT (Also called WIT-Real) and YouTube-Audio (Also YT-Audio-Real) datasets, which are widely employed in existing hybrid querying algorithm research. These datasets feature real attribute information and have been broadly accepted by the community as standard benchmarks for evaluating hybrid query performance.  For more details, please refer to our response to Meta R3.

In addition, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the performance of algorithms. For more details, please refer to our response to Review 1 W1.

In order to further verify the performance of these algorithms in real scenarios, we have conducted experiments on these two datasets with real attributes and have analyzed the experimental results. \textbf{(Please see Section 4.2 and  Section 4.3,  highlighted in blue in the revised manuscript.).}

### 2025-07-31 VLDB2026/main.tex
Update main.tex

	\section{CONCLUSION}
	In this paper, we systematically evaluate various hybrid query methods, including multiple algorithms, vector databases, and libraries. We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm. Experiments show that existing algorithms still have significant shortcomings when facing challenges such as large-scale data, complex queries, and resource constraints. There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms. Furthermore, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries. Notably, in some high-recall scenarios, some algorithms even perform worse than the baseline method (e.g., Faiss). In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction. Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.
%	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries. We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm. Experiments show that these algorithms still have shortcomings in scenarios such as large-scale data, complex queries, and resource constraints. There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms. Additionally, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries. Notably, some algorithms even perform worse than the baseline method (e.g., Faiss) in high recall scenarios.  In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction. Furthermore, in many real-time scenarios, both attribute and range filtering are required simultaneously, and therefore, exploring algorithms that support a combination of both is also an important research topic.
%	In the future, it is essential to further explore the flexibility and robustness of attribute filtering algorithms, and improving the performance of range filtering algorithms remains an important direction.
%	\textcolor{blue}{
%		In this paper, we evaluate hybrid query methods, including algorithms, vector databases, and libraries. We design experiments to assess the performance of attribute filtering algorithms. We enrich existing datasets with attribute values and create various experimental scenarios to ensure fair comparisons. We run experiments on 7 real-world datasets to analyze the effectiveness of attribute filtering algorithms. We also compare range filtering algorithms using 4 range query datasets. Finally, we analyze the results, summarize key findings, and identify areas for improvement. Our study validates previous research and provides insights for future work.
%	}
%

>>>>

	\section{CONCLUSION}
	In this paper, we systematically evaluate various hybrid query methods, including multiple algorithms, vector databases, and libraries. We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm. Experiments show that existing algorithms still have significant shortcomings in scenarios such as large-scale data, complex queries, and resource constraints. There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms. Furthermore, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries. Notably, in some high-recall scenarios, some algorithms even perform worse than the baseline method (e.g., Faiss). In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction. Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.
%	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries. We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm. Experiments show that these algorithms still have shortcomings in scenarios such as large-scale data, complex queries, and resource constraints. There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms. Additionally, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries. Notably, some algorithms even perform worse than the baseline method (e.g., Faiss) in high recall scenarios.  In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction. Furthermore, in many real-time scenarios, both attribute and range filtering are required simultaneously, and therefore, exploring algorithms that support a combination of both is also an important research topic.
%	In the future, it is essential to further explore the flexibility and robustness of attribute filtering algorithms, and improving the performance of range filtering algorithms remains an important direction.
%	\textcolor{blue}{
%		In this paper, we evaluate hybrid query methods, including algorithms, vector databases, and libraries. We design experiments to assess the performance of attribute filtering algorithms. We enrich existing datasets with attribute values and create various experimental scenarios to ensure fair comparisons. We run experiments on 7 real-world datasets to analyze the effectiveness of attribute filtering algorithms. We also compare range filtering algorithms using 4 range query datasets. Finally, we analyze the results, summarize key findings, and identify areas for improvement. Our study validates previous research and provides insights for future work.
%	}
%
